---
title: "ocpuppy"
author: "Bobby Fatemi"
date: "April 25, 2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_engines$set(python = reticulate::eng_python)
```

## Python Client for Cortex API
```{python, cache=TRUE}
import requests

def _url():
    return 'http://104.248.133.93'

def api_url(path):
    return _url() + '/ocpu/user/intusurg/library/api/R/' + path


def list_api_functions():
  return requests.get(api_url('')).content
  

def cortex_api(fun, args):
  H = {'Content-Type':'application/json'} # header
  url = api_url(fun) # url for r function call
  r = requests.post(url, json = args, headers=H) # call fun passing json formatted args
  return(r)


def cortex_post(fun, args):
  H = {'Content-Type':'application/json'} # header
  url = api_url(fun) # url for r function call
  r = requests.post(url, json = args, headers=H) # call fun passing json formatted args
  assert(r.status_code == 201), "API ERROR"
  return(r.headers['X-ocpu-session'])


def cortex_session(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID
  r = requests.get(url, headers = H)
  return(r.content)

def cortex_session_fun(SID, fun):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/R/" + fun
  r = requests.get(url, headers = H)
  return(r.text)
  

def cortex_session_value(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/R/.val/json"
  r = requests.get(url, headers = H)
  return(r.json())
  
  
def cortex_session_console(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/console/json"
  r = requests.get(url, headers = H)
  return(r.json())

def cortex_session_stdout(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/stdout/json"
  r = requests.get(url, headers = H)
  return(r.json())


def cortex_session_info(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/info"
  r = requests.get(url, headers = H)
  return(r.content)

def cortex_session_package(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/files/DESCRIPTION"
  r = requests.get(url, headers = H)
  return(r.content)


def cortex_session_source(SID):
  H = {'Content-Type':'application/json'} # header
  url = _url() + "/ocpu/tmp/" + SID + "/source/json"
  r = requests.get(url, headers = H)
  return(r.json())

def R(fun, args):
  H = {'Content-Type':'application/json'}
  r1 = cortex_api(fun, args)
  assert(r1.status_code == 201), "API ERROR"
  val_url = _url() + r1.content.split()[0] + "/json"
  r2 = requests.get(val_url)
  return(r2.json())

#resp = cortex_api("rFunction1", {'opt': 'value'})
#print(resp.content)

rfun = "rFunction1"
args = {'opt': 'value'}

SID = cortex_post(rfun, args)

print(cortex_session(SID))
print(cortex_session_value(SID))
print(cortex_session_info(SID))
print(cortex_session_package(SID))
print(cortex_session_source(SID))
print(cortex_session_stdout(SID))
print(cortex_session_console(SID))
print(cortex_session_fun(SID, rfun))
```






print(cortex_session_function(SID))



session_objects = cortex_session(SID)
print(session_objects)

val = cortex_session_value(SID)

cortex_session_stdout(SID)
cortex_session_console(SID)
cortex_session_info(SID)
cortex_session_package(SID)
print(val)

output = R("rFunction1", {'opt': 'value'})
print(output)





  

  
session = 


val_path = session
print(val_path)

value = cortex_get(val_path)
print(value)

```

## Cortex Analytics

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
